---
title: "ReprodResearch1"
author: "SK"
date: "Sunday, November 16, 2014"
output: html_document
---
Read in data and format for use.
```{r, setoptions, echo = TRUE}
activity <- read.csv("~/R_work/ReprodResearch1.csv")
good_data.df<- data.frame(activity[complete.cases(activity), ])  # activity without NA rows
good_data.df$date <- as.Date(good_data.df$date) # get date col in date format
```
Calculate mean, median, sum
```{r}
agg_mean <- aggregate(x=good_data.df[c("steps","interval")], by=list(good_data.df$date), FUN="mean")
agg_median <- aggregate(x=good_data.df[c("steps","interval")], by=list(good_data.df$date), FUN="median") 
agg_sum <- aggregate(x=good_data.df[c("steps","interval")], by=list(good_data.df$date), FUN="sum") 
agg_avg_time <- aggregate(x=good_data.df[c("steps","interval")], by=list(good_data.df$interval), FUN="mean")
```
Histogram of sum per day

```{r}
hist(agg_sum$steps)
```
Mean of steps per day
```{r}
agg_mean
```
Median steps per day
```{r}
agg_median
```
Time series plot
```{r}
library(lattice)
xyplot(agg_avg_time$steps ~ agg_avg_time$interval, data = agg_avg_time,type = "l")
```
Total missing numbers in steps
```{r}
num_na <-sum(is.na(activity$steps))
```
Replace na with 0.
Recalculate mean, median, and sum
```{r}
for (i in 1:17568){
 if (is.na(activity$steps[i])) {
     activity$steps[i] <- 0
  }
}
  
agg_mean_tot <- aggregate(x=activity[c("steps","interval")], by=list(activity$date), FUN="mean")
agg_median_tot <- aggregate(x=activity[c("steps","interval")], by=list(activity$date), FUN="median") 
agg_sum_tot <- aggregate(x=activity[c("steps","interval")], by=list(activity$date), FUN="sum") 
agg_avg_time_tot <- aggregate(x=activity[c("steps","interval")], by=list(activity$interval), FUN="mean")
```
Mean steps per day
```{r}
agg_mean_tot
```
Median steps per day
```{r}
agg_median_tot
```
Histogram of sum of steps per day
```{r}
hist(agg_sum_tot$steps)
```
Inputing values for the NAs has impacted results by adding more zero step intervals.
Tried to identify weekdays from weekends using:
activity$date <- as.Date(activity$date)
for (i in 1:17568){
  activity$day[i]<-weekdays(activity$date[i])
  if (isTRUE(all.equal(activity$day[i] == "Saturday" | "Sunday")){
    activity$w[i]<-1
  }else{activity$w[i]<-0}
}
